A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-05-27 paper/paper.tex
line numbers

% ============================================================
\begin{document}
\maketitle
% ==================================================================

@@

\paragraph{Structure of the paper:}
The remainder of this paper is structured as follows. Section~\ref{sec:relatedwork} overviews related works. 
%In Section~\ref{sec:preliminaries}, we introduce preliminary notions and the notation used throughout the paper. 
Our algorithm is presented in detail in Section~\ref{sec:algorithm} and is experimentally evaluated against the ones of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} and Argyriou at al.~\cite{DBLP:journals/cj/ArgyriouBS13} in Section~\ref{sec:experiments}. We conclude in Section~\ref{sec:conclusions} with interesting open problems and future~directions.

@@

More concretely, from an applicative point of view, Didimo et al.~\cite{DBLP:conf/apvis/DidimoLR10} describe a system, called \emph{COWA}, to support conceptual web site traffic analysis, whose algorithmic core is a force-directed heuristic to compute simultaneous embeddings of two non-planar graphs with high crossing resolution. 
%
In a follow up work, Didimo et al.~\cite{DBLP:conf/gd/DidimoLR10} describe heuristics, designed within the topology-driven force-directed framework, to achieve good trade-offs in terms of number of edge crossings, crossing resolution, and geodesic edge tendency. 
%
However, the obtained drawings are not straight-line. For straight-line drawings, Nguyen et al.~\cite{DBLP:conf/gd/NguyenEHH10} suggest a quadratic-programming based approach to increase the crossing angles of circular drawings. 
%
Of more general scope are the already mentioned works of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} and Argyriou at al.~\cite{DBLP:journals/cj/ArgyriouBS13}, which are both based on the force-directed technique.

>>>>

% ============================================================
\begin{document}
\maketitle
\linenumbers
% ==================================================================

@@

\paragraph{Structure of the paper:}
The remainder of this paper is structured as follows. Section~\ref{sec:relatedwork} overviews related works. 
%In Section~\ref{sec:preliminaries}, we introduce preliminary notions and the notation used throughout the paper. 
Our algorithm is presented in detail in Section~\ref{sec:algorithm} and is experimentally evaluated against the ones of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} and Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13} in Section~\ref{sec:experiments}. We conclude in Section~\ref{sec:conclusions} with interesting open problems and future~directions.

@@

More concretely, from an applicative point of view, Didimo et al.~\cite{DBLP:conf/apvis/DidimoLR10} describe a system, called \emph{COWA}, to support conceptual web site traffic analysis, whose algorithmic core is a force-directed heuristic to compute simultaneous embeddings of two non-planar graphs with high crossing resolution. 
%
In a follow up work, Didimo et al.~\cite{DBLP:conf/gd/DidimoLR10} describe heuristics, designed within the topology-driven force-directed framework, to achieve good trade-offs in terms of number of edge crossings, crossing resolution, and geodesic edge tendency. 
%
However, the obtained drawings are not straight-line. For straight-line drawings, Nguyen et al.~\cite{DBLP:conf/gd/NguyenEHH10} suggest a quadratic-programming based approach to increase the crossing angles of circular drawings. 
%
Of more general scope are the already mentioned works of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} and Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13}, which are also based on the force-directed technique.
